Redshift Evolution of the Underlying Type Ia Supernova Stretch Distribution

### 2020-06-26 referee_answer.tex

\begin{figure}[htbp!]
    \centering
    \begin{subfigure}[t]{0.49\linewidth}
        \centering
        \includegraphics[width=\linewidth]{Answer_figures/mean_stretchs-nHST_full-sup.pdf}
    \end{subfigure}
    \begin{subfigure}[t]{0.49\linewidth}
        \centering
        \includegraphics[width=\linewidth]{Answer_figures/mean_colors-nHST_full-sup.pdf}
    \end{subfigure}
    \centering
    \captionsetup{justification=centering, size=small}
    \caption{Mean stretch and color of the complete sample in the same 6 bins of
        equal sample size (based on the fiducial sample). The dark grey markers
        represent the full, uncut sample; the light grey ones the fiducial
        sample; the SNe above the fiducial cut are in green; in transparent
        light grey is the conservative sample and the open marker shows the
        means for the complete sample from which we removed HST data. For the
        color, we might think that there is an evolution for the 5 first bins,
        but the 6th one breaks it, even without HST data, while for the stretch,
    with our without HST data we see the same evolution}
    \label{fig:means}
\end{figure}

\section{Of the $x_1$ drift of simulated surveys}
A full SNANA analysis will soon be ongoing and should be the subject of a
dedicated paper, giving more indepth insight concerning the simulations
thoughts that were shared with us.

### 2020-06-30 referee_answer.tex

\begin{figure}[htbp!]
    \centering
    \begin{subfigure}[t]{0.49\linewidth}
        \centering
        \includegraphics[width=\linewidth]{Answer_figures/mean_stretchs-nHST_full-sup.pdf}
    \end{subfigure}
    \begin{subfigure}[t]{0.49\linewidth}
        \centering
        \includegraphics[width=\linewidth]{Answer_figures/mean_colors-nHST_full-sup.pdf}
    \end{subfigure}
    \centering
    \captionsetup{justification=centering, size=small}
    \caption{Mean stretch and color of the complete sample in the same 6 bins of
        equal sample size (based on the fiducial sample). The dark grey markers
        represent the full, uncut sample; the light grey ones the fiducial
        sample; the SNe above the fiducial cut are in green; in transparent
        light grey is the conservative sample and the open marker shows the
        means for the complete sample from which we removed HST data. For the
        color, we might think that there is an evolution for the 5 first bins,
        but the 6th one breaks it, even without HST data, while for the stretch,
    with our without HST data we see the same evolution}
    \label{fig:means}
\end{figure}

\section{Of the $x_1$ drift of simulated surveys}
We recall here that a full SNANA analysis will soon be ongoing and should be the
subject of a dedicated paper, giving more indepth insight concerning the
simulations thoughts that were shared with us. \bigbreak

The referee pointed out that simulated samples without drift parameters do
recover a stretch evolution, saying that the $x_1$ drift could be entirely
explained by selection effects. We agree that both our supposed drift and
selection effects go the same way, so it seems natural to see this trend in
other studies. However, concerning the Fig. 6 of \textsc{Mosher et al.} 2014
which uses SDSS data we see that this trend actually goes up, according to
selection effects, only after $z > 0.2$, which corresponds to our redshift cut
for that survey. We feel that the plots the referee showed us are mostly
examples that simulated samples include both drift and selection effects, the
two of them stacking at the end of the redshift range. \bigbreak

Concerning the inclusion of the Per sample Asym model without using simulations
beforehand, we want to point out that the idea is actually to compare models
prescribing a drift parameter with those that don't, using pertinent models
(Howell, Per sample Asym for instance). The Per sample Asym model is used in
current cosmological studies and was said by their authors to be able to account
for unmodeled redshift drifts thanks to the limited span of the surveys: we
also wanted to test this affirmation. It would seem that this model is relevant
for this study. \bigbreak

\section{General comments}
The parameters comparison in the referee's comments are indeed not agreeing with
each other. There may be two reasons for that:
\begin{enumerate}

    \item Even if we work on the same surveys, the datasets we use are really
        different from \textsc{Scolnic \& Kessler} 2016 because they worked on
        their corrected full sample while we used a subset of that through the
        redshift cuts; differences in the computed parameters are expected in
        that matter.

    \item Moreover, the parameters we say are in really good agreement are those
        of PS1 from \textsc{Scolnic \& Kessler} \underline{2018}, in which they
        presented updated results that are in much better agreement with ours;
        we suspect that the same work done for SNLS and SDSS would go the same
        way.

\end{enumerate}

### 2020-06-30 Nicolas.tex
Update

\newcommand{\prob}[2]{\mathcal{P}\left( #1 \mid #2\right)}

@@

\author{
    N. Nicolas \thanks{n.nicolas@ipnl.in2p3.fr, equal contribution} \inst{1} 
    \and M. Rigault \thanks{m.rigault@ipnl.in2p3.fr, equal contribution} \inst{2}
    \orcid{0000-0002-8121-2560}
    \and\\ Y. Copin \inst{1}
    \orcid{0000-0002-5317-7518}
    \and R. Graziani \inst{2}
    \and G. Aldering\inst{3}
    \and M. Briday\inst{1}
    \and J. Nordin\inst{4}
    \and Y.-L. Kim\inst{1}
    \orcid{0000-0002-1031-0796}
    \and Saul Perlmutter\inst{3}
}

\institute{Université de Lyon, F-69622, Lyon, France; Université de Lyon
    1, Villeurbanne; CNRS/IN2P3, Institut de Physique des Deux Infinis, Lyon
    \and 
    Université Clermont Auvergne, CNRS/IN2P3, Laboratoire de
    Physique de Clermont, F-63000 Clermont-Ferrand, France.
    \and
    Physics Division, Lawrence Berkeley National Laboratory, 
    1 Cyclotron Road, Berkeley, CA, 94720 
    \and
    Institut fur Physik, Humboldt-Universität zu Berlin, Newtonstr. 15,
    12489 Berlin
}

@@

\section{Complete Sample Construction}\label{sec:sample}

@@

>>>>

\newcommand{\nn}[1]{\textcolor[rgb]{0.25, 0.50, 0}{#1}}
\newcommand{\prob}[2]{\mathcal{P}\left( #1 \mid #2\right)}

@@

\author{
    N. Nicolas \thanks{n.nicolas@ipnl.in2p3.fr, equal contribution} \inst{1} 
    \and M. Rigault \thanks{m.rigault@ipnl.in2p3.fr, equal contribution} \inst{2}
    \orcid{0000-0002-8121-2560}
    \and\\ Y. Copin \inst{1}
    \orcid{0000-0002-5317-7518}
    \and R. Graziani \inst{2}
    \and G. Aldering\inst{3}
    \and M. Briday\inst{1}
    \and J. Nordin\inst{4}
    \and Y.-L. Kim\inst{1}
    \orcid{0000-0002-1031-0796}
    \and Saul Perlmutter\inst{3}
    \and M. Smith\inst{4}
    \orcid{0000-0002-3321-1432}
}

\institute{Université de Lyon, F-69622, Lyon, France; Université de Lyon
    1, Villeurbanne; CNRS/IN2P3, Institut de Physique des Deux Infinis, Lyon
    \and 
    Université Clermont Auvergne, CNRS/IN2P3, Laboratoire de
    Physique de Clermont, F-63000 Clermont-Ferrand, France.
    \and
    Physics Division, Lawrence Berkeley National Laboratory, 
    1 Cyclotron Road, Berkeley, CA, 94720 
    \and
    Institut fur Physik, Humboldt-Universität zu Berlin, Newtonstr. 15,
    12489 Berlin
    \and
    University of Southampton: Southampton, GB
}

@@

\section{Complete Sample Construction}\label{sec:sample}
\subsection{\nn{Applying redshift cuts}}\label{ssec:cuts}

@@

\subsection{\nn{Verifying completeness}}\label{ssec:verify}

\nn{In order to ensure that the effects we model are only due to the supposed drift,
we need to check for possible Malmquist bias left in the sample. Because color
is most sensitive to selection effects, we studied both the stretch and color of
the end of SDSS and the start of PS1, for $0.10 < z < 0.20$. In this redshift
range, because the SDSS SNe between $0.15 < z < 0.20$ are between our
conservative and fiducial cuts, these SNe are the most prone to have selection
effects. However, the PS1 dataset is quite robust because these SNe are far from
both the conservative and fiducial cuts; see Fig. \ref{fig:cuts}.}

\nn{The results are shown Fig. \ref{fig:distrib}. We represented the normed
histograms along with their error bars, and found that they don't differ much.
To ascertain this idea, we used a Kolmogorov-Smirnov test that gave us a p-value
of $0.265$ for the color, and $0.137$ for the stretch; while it doesn't tell us
that both the SDSS and PS1 parts come from the same distribution, as would be
expected if we were free from selection effects (so that the samples were random
draws from what Nature could give us), it is not excluded. }

\begin{figure*}
    \centering
    \includegraphics[width=17cm]{Article_figures/both-cut_SDSS_PS1-010-020.pdf}
    \caption{\nn{$x_1$ and $c$ normed histograms of the SDSS and PS1 samples for
        $0.10 < z < 0.20$ and their errorbars. On the left, we find in orange
        lines the Base model distributions for $z = 0.10, 0.15, 0.20$ from top
        to bottom. The p-values are the results from a Kolmogorov-Smirnov test;
    they don't show any indication that the samples are not taken from the same
distribution, for both $c$ and $x_1$.}}
    \label{fig:distrib}
\end{figure*}
